On exponential sums arising from the classical doubling method

### 2025-03-28 main.tex
Update from Overleaf

%% frequently used symbols
% Common math notions
\newcommand{\zIntegers}{\mathbb{Z}}
\newcommand{\rReal}{\mathbb{R}}
\newcommand{\cComplex}{\mathbb{C}}
\newcommand{\multiplicativegroup}[1]{#1^{\times}}
\newcommand{\RealPart}{\mathrm{Re}}
\newcommand{\detQuadratic}{{\det}_{\quadraticExtension}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\EndomorphismRing}{\operatorname{End}}
\newcommand{\Span}{\mathrm{span}}
\newcommand{\Supp}{\mathrm{supp}}
\newcommand{\Stab}{\mathrm{stab}}
\newcommand{\idmap}{\mathrm{id}}
\newcommand{\conjugate}[1]{\overline{#1}}
\newcommand{\indicatorFunction}[1]{\delta_{#1}}
\newcommand{\isomorphic}{\cong}
\newcommand{\lengthof}{\mathfrak{n}}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\sizeof}[1]{\left|#1\right|}
\newcommand{\lcm}{\operatorname{lcm}}
\newcommand{\hermitianSpace}{\mathrm{V}}
\newcommand{\xIsotropic}{\mathrm{X}}
\newcommand{\yIsotropic}{\mathrm{Y}}
\newcommand{\similitudeCharacter}{\operatorname{sim}}

@@

\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblJacobiSumScalar}[2]{\mathrm{J}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\negDblJacobiSumScalar}[2]{\mathrm{J}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblPosVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblNegVirtualJacobiSumScalar}[2]{\mathrm{j}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\dblLanglandsGammaFactorSpace}[4]{\gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}
\newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
\newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
\newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}
\newcommand{\DualFrobeniusFixedPoints}[2][\Frobenius^{\ast}]{\algebraicGroup{#2}^{\ast #1}}
\newcommand{\FrobeniusFixedPoints}[2][\Frobenius]{\algebraicGroup{#2}^{#1}}
\newcommand{\CharacterLattice}[1]{X^{\ast}\left(#1\right)}
\newcommand{\CocharacterLattice}[1]{X_{\ast}\left(#1\right)}

@@

We are now ready to state Kondo's result.
\begin{theorem}[Kondo {\cite{Kondo1963}}]
	Suppose that $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ with cuspidal support $\left\{\tau_1,\dots, \tau_r\right\}$, where $n_1 + \dots + n_r = n$, and where for every $j$, $\tau_j$ is an irreducible cuspidal representation of $\GL_{n_j}\left(\finiteField\right)$ corresponding to the Frobenius orbit of a regular character $\theta_j \colon \multiplicativegroup{\finiteFieldExtension{n_j}} \to \multiplicativegroup{\cComplex}$. Then
	$$\GaussSumScalar{\tau \times \chi}{\fieldCharacter} = \left(-1\right)^n \cdot \prod_{j=1}^r \GaussSumCharacter{\theta_j}{\chi}{\fieldCharacter_{n_j}}.$$
\end{theorem}

@@

\subsubsection{Rational Tori}
A \emph{rational torus} $\algebraicGroup{T} \subset \algebraicGroup{G}$ over $\finiteField$ is a torus defined over $\finiteField$. 
Over a finite field, $\algebraicGroup{G}(\finiteField)$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group. In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\finiteField})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\finiteField)$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$, see \cite[Section 3.3]{Carter1985}.

@@

Let $\algebraicGroup{A}_n \subset \algebraicGroup{\GL}_n$ be the diagonal torus. We denote for an element $g \in \algebraicGroup{\GL}_n$, $g^{\ast} = w_n \transpose{g}^{-1} w_n$, where $w_n$ is the long Weyl element (see \Cref{subsec:isometry-groups}). Using $\algebraicGroup{A}_n$ we define standard (mostly split) tori in our groups as follows.
\begin{center}
\begin{tabular}{|c|c|}
	\hline 
		$\algebraicGroup{G}$ & $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ \tabularnewline
		\hline 
		\hline 
		$\algebraicGroup{\UnitaryGroup}_{2n}$ & $\left\{ \begin{pmatrix}
			a\\
			& \involution{\left(a^{\ast}\right)}
		\end{pmatrix}  \mid a \in \algebraicGroup{A}_n \right\}$ \tabularnewline
		\hline 
		$\algebraicGroup{\UnitaryGroup}_{2n+1}$ & $\left\{ \begin{pmatrix}
	a \\
	& t\\
	& & \involution{\left(a^{\ast}\right)}
\end{pmatrix}  \mid a \in \algebraicGroup{A}_n,\,\, t \in \algebraicGroup{U}_1 \right\}$ \tabularnewline
\hline 
	$\algebraicGroup{\SO}_{2n+1}$ & $\left\{ \begin{pmatrix}
		a\\
		& 1\\
		& & a^{\ast}
	\end{pmatrix} \mid a \in \algebraicGroup{A}_n \right\}$ \tabularnewline
	\hline 
	$\algebraicGroup{\Sp}_{2n}$ or $\algebraicGroup{\SO}^{+}_{2n}$ & $\left\{ \begin{pmatrix}
		a\\
		& a^{\ast}
	\end{pmatrix} \mid a \in \algebraicGroup{A}_n \right\}$ \tabularnewline
	\hline 
	$\algebraicGroup{\SO}_{2n}^{-}$ & $\left\{ \begin{pmatrix}
		a\\
		& h\\
		& & a^{\ast}
	\end{pmatrix} \mid a \in \algebraicGroup{A}_{n-1}\,\, h \in \algebraicGroup{\SO}_2^{-} \right\}$ \tabularnewline
	\hline		
	\end{tabular}
\end{center}
Here, $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ is split for all rows except for the last row. We also write down the standard tori for the relevant corresponding similitude groups.
\begin{center}
	\begin{tabular}{|c|c|}
		\hline 
		$\algebraicGroup{G}$ & $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ \tabularnewline
		\hline 
		\hline 
		$\algebraicGroup{\GSp}_{2n}$ or $\algebraicGroup{\GSO}^{+}_{2n}$ & $\left\{\left(\begin{pmatrix}
			\lambda a\\
			& a^{\ast}
		\end{pmatrix}, \lambda\right) \mid a \in \algebraicGroup{A}_n,\,\, \lambda \in \multiplcativeScheme \right\}$ \tabularnewline
		\hline 
		$\algebraicGroup{\GSO}_{2n}^{-}$ & $\left\{ \left(\begin{pmatrix}
			\algebraicGroup{\aFieldNorm}_{\finiteFieldExtension{2} \slash \finiteField}\left(h\right) a\\
			& h\\
			& & a^{\ast}
		\end{pmatrix}, \algebraicGroup{\aFieldNorm}_{\finiteFieldExtension{2} \slash \finiteField}\left(h\right)\right) \mid a \in \algebraicGroup{A}_{n-1}\,\, h \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \right\}$ \tabularnewline
		\hline		
	\end{tabular}
\end{center}
Here we realize $\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ as $$\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} = \left\{ \left(\begin{pmatrix}
	a & b\\
	db & a
\end{pmatrix}, \lambda\right) \mid a^2 - db^2 = \lambda \in \multiplcativeScheme \right\},$$
where $d$ is as in \Cref{subsec:isometry-groups}.

In the unitary case, the action of $\Frobenius$ on $W(\algebraicGroup{T}_{\algebraicGroup{U}}^{std})$ is conjugation by $w_n$. In the $\algebraicGroup{SO}^-_{2n}$ case, the action of $\Frobenius$ on $W(\algebraicGroup{T}_{\algebraicGroup{U}}^{std})$ is the outer automorphism on the Dynkin diagram of type D. In terms of signed permutations with an even number of negative signs this corresponds to conjugation by the transposition $(-1,1)$ \calvin{or the $(-n,n)$. Kinda depends on conventions. The most correct thing to say is it corresponds to conjugation by the matrix $\begin{pmatrix} I_{n-1} & 0 & 0&0 \\ 0 &0&1&0\\0&1&0&0\\0&0&0&I_{n-1}\end{pmatrix}$}. In all other cases, the action of $\Frobenius$ on $W(\algebraicGroup{T}_{\algebraicGroup{U}}^{std})$ is trivial. We now parameterize the Weyl group $\Frobenius$-twisted conjugacy classes and their corresponding tori:

\begin{enumerate}
    \item (Type A: Unitary groups) The map $w \mapsto w\cdot w_n$ sends a $w_n$-twisted $S_n$ conjugacy class to an $S_n$ conjugacy class. Thus twisted conjugacy classes are determined by the cycle partition $\lambda$ associated to $w\cdot w_n$. The corresponding algebraic torus is \calvin{$L$ is the lang map}
	$$^{L^{-1}w}\algebraicGroup{T} =\prod_{i} \begin{dcases}
	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} & \lambda_i \textnormal{ is even} \\
	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}  & \lambda_i \textnormal{ is odd}
	\end{dcases}$$
    \item (Type B, C, D: Special orthogonal and symplectic groups)
    Conjugacy classes in the type B Weyl (signed permutations) group are classified by pairs of partitions $(\lambda^+,\lambda^-)$.
	\begin{enumerate}[(a)]
        \item ($\algebraicGroup{SO}_{2n+1}$ or $\algebraicGroup{Sp}$) Let $(\lambda^+,\lambda^-)$ correspond to the conjugacy class of $w$. Then
		$$^{L^{-1}w}\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
        \item ($\algebraicGroup{SO}_{2n}^+$) Viewing the type D Weyl (even signed permutations) group as a subgroup of signed permutations, we can associate to a $(\lambda^+,\lambda^-)$ pair via the conjugacy class of $w$. Then
		$$^{L^{-1}w}\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
		\item ($\algebraicGroup{SO}_{2n}^-$) The map $w \mapsto w\circ (-1,1)$ sends a $(-1,1)$-twisted conjugacy class in the even signed permutation group to a conjugacy class in the signed permutation group. Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $w\circ (-1,1)$. Then
		$$^{L^{-1}w}\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
	\end{enumerate}
	\item (Type C,D similitude groups)
        \begin{enumerate}[(a)]
        \item ($\algebraicGroup{GSp}$ or $\algebraicGroup{GSO}_{2n}^+$) Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $w$. Then \calvin{probably should have an alternate description}
        $$^{L^{-1}w}\algebraicGroup{T} = \{(\vec{x},\vec{y},\lambda) \in  \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme\} | \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = \lambda \textnormal{ for all }y_i\}$$
		\item ($\algebraicGroup{SO}_{2n}^-$) Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $w\circ (-1,1)$. Then
		$$^{L^{-1}w}\algebraicGroup{T} = \{(\vec{x},\vec{y},\lambda) \in  \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme\} | \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = \lambda \textnormal{ for all }y_i\}$$
        \end{enumerate}
\end{enumerate}

>>>>

%% frequently used symbols
% Common math notions
\newcommand{\zIntegers}{\mathbb{Z}}
\newcommand{\rReal}{\mathbb{R}}
\newcommand{\cComplex}{\mathbb{C}}
\newcommand{\multiplicativegroup}[1]{#1^{\times}}
\newcommand{\RealPart}{\mathrm{Re}}
\newcommand{\detQuadratic}{{\det}_{\quadraticExtension}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\EndomorphismRing}{\operatorname{End}}
\newcommand{\Span}{\mathrm{span}}
\newcommand{\Supp}{\mathrm{supp}}
\newcommand{\Stab}{\mathrm{stab}}
\newcommand{\idmap}{\mathrm{id}}
\newcommand{\conjugate}[1]{\overline{#1}}
\newcommand{\indicatorFunction}[1]{\delta_{#1}}
\newcommand{\isomorphic}{\cong}
\newcommand{\lengthof}{\ell}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\sizeof}[1]{\left|#1\right|}
\newcommand{\lcm}{\operatorname{lcm}}
\newcommand{\hermitianSpace}{\mathrm{V}}
\newcommand{\xIsotropic}{\mathrm{X}}
\newcommand{\yIsotropic}{\mathrm{Y}}
\newcommand{\similitudeCharacter}{\operatorname{sim}}

@@

\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblJacobiSumScalar}[2]{\mathrm{J}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\negDblJacobiSumScalar}[2]{\mathrm{J}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblPosVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblNegVirtualJacobiSumScalar}[2]{\mathrm{j}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\dblLanglandsGammaFactorSpace}[4]{\gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\IsometryGroup}{\mathrm{Isom}}
\newcommand{\lieAlgebra}{\mathfrak{g}}
\newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
\newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
\newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
\newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}
\newcommand{\DualFrobeniusFixedPoints}[2][\Frobenius^{\ast}]{\algebraicGroup{#2}^{\ast #1}}
\newcommand{\FrobeniusFixedPoints}[2][\Frobenius]{\algebraicGroup{#2}^{#1}}
\newcommand{\CharacterLattice}[1]{X^{\ast}\left(#1\right)}
\newcommand{\CocharacterLattice}[1]{X_{\ast}\left(#1\right)}
\newcommand{\SymmetricGroup}{\mathfrak{S}}

@@

We are now ready to state Kondo's result.
%test
\begin{theorem}[Kondo {\cite{Kondo1963}}]
	Suppose that $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ with cuspidal support $\left\{\tau_1,\dots, \tau_r\right\}$, where $n_1 + \dots + n_r = n$, and where for every $j$, $\tau_j$ is an irreducible cuspidal representation of $\GL_{n_j}\left(\finiteField\right)$ corresponding to the Frobenius orbit of a regular character $\theta_j \colon \multiplicativegroup{\finiteFieldExtension{n_j}} \to \multiplicativegroup{\cComplex}$. Then
	$$\GaussSumScalar{\tau \times \chi}{\fieldCharacter} = \left(-1\right)^n \cdot \prod_{j=1}^r \GaussSumCharacter{\theta_j}{\chi}{\fieldCharacter_{n_j}}.$$
\end{theorem}

@@

\subsubsection{Rational Tori}
A \emph{rational torus} $\algebraicGroup{T} \subset \algebraicGroup{G}$ over $\finiteField$ is a torus defined over $\finiteField$. 
Over a finite field, $\algebraicGroup{G}(\finiteField)$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group. In particular if we fix a rational torus $\algebraicGroup{T}_0$ with rank $\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\finiteField})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and its $\algebraicGroup{G}(\finiteField)$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of the Lang map $L \colon \algebraicGroup{G}\left(\algebraicClosure{\finiteField}\right) \to \algebraicGroup{G}\left(\algebraicClosure{\finiteField}\right)$ defined as $L\left(g\right) = g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$, see \cite[Section 3.3]{Carter1985}.

@@

Let us denote $$\left(\quadraticExtension, x \mapsto \involution{x}\right) = \begin{dcases}
	\left(\finiteFieldExtension{2}, x \mapsto x^q\right)  & \algebraicGroup{G} \text{ is a unitary group},\\
	\left(\finiteField, x \mapsto x\right) & \text{otherwise.}
\end{dcases}$$

Let $\algebraicGroup{A}_n \subset \algebraicGroup{\GL}_n$ be the diagonal torus. We denote for an element $g \in \algebraicGroup{\GL}_n$, $g^{\ast} = w_n \transpose{g}^{-1} w_n$, where $w_n$ is the long Weyl element (see \Cref{subsec:isometry-groups}). Using $\algebraicGroup{A}_n$ we define standard (mostly split) tori in our groups as follows.
\begin{center}
\begin{tabular}{|c|c|}
	\hline 
		$\algebraicGroup{G}$ & $\algebraicGroup{T}_0$ \tabularnewline
		\hline 
		\hline 
		$\algebraicGroup{\UnitaryGroup}_{2n}$ & $\left\{ \begin{pmatrix}
			a\\
			& \involution{\left(a^{\ast}\right)}
		\end{pmatrix}  \mid a \in \algebraicGroup{A}_n \right\}$ \tabularnewline
		\hline 
		$\algebraicGroup{\UnitaryGroup}_{2n+1}$ & $\left\{ \begin{pmatrix}
	a \\
	& t\\
	& & \involution{\left(a^{\ast}\right)}
\end{pmatrix}  \mid a \in \algebraicGroup{A}_n,\,\, t \in \algebraicGroup{U}_1 \right\}$ \tabularnewline
\hline 
	$\algebraicGroup{\SO}_{2n+1}$ & $\left\{ \begin{pmatrix}
		a\\
		& 1\\
		& & a^{\ast}
	\end{pmatrix} \mid a \in \algebraicGroup{A}_n \right\}$ \tabularnewline
	\hline 
	$\algebraicGroup{\Sp}_{2n}$ or $\algebraicGroup{\SO}^{+}_{2n}$ & $\left\{ \begin{pmatrix}
		a\\
		& a^{\ast}
	\end{pmatrix} \mid a \in \algebraicGroup{A}_n \right\}$ \tabularnewline
	\hline 
	$\algebraicGroup{\SO}_{2n}^{-}$ & $\left\{ \begin{pmatrix}
		a\\
		& h\\
		& & a^{\ast}
	\end{pmatrix} \mid a \in \algebraicGroup{A}_{n-1}\,\, h \in \algebraicGroup{\SO}_2^{-} \right\}$ \tabularnewline
	\hline		
	\end{tabular}
\end{center}
Here, $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ is split for all rows except for the last row. We also write down the standard tori for the relevant corresponding similitude groups.
\begin{center}
	\begin{tabular}{|c|c|}
		\hline 
		$\algebraicGroup{G}$ & $\algebraicGroup{T}_0$ \tabularnewline
		\hline 
		\hline 
		$\algebraicGroup{\GSp}_{2n}$ or $\algebraicGroup{\GSO}^{+}_{2n}$ & $\left\{\left(\begin{pmatrix}
			\lambda a\\
			& a^{\ast}
		\end{pmatrix}, \lambda\right) \mid a \in \algebraicGroup{A}_n,\,\, \lambda \in \multiplcativeScheme \right\}$ \tabularnewline
		\hline 
		$\algebraicGroup{\GSO}_{2n}^{-}$ & $\left\{ \left(\begin{pmatrix}
			\algebraicGroup{\aFieldNorm}_{\finiteFieldExtension{2} \slash \finiteField}\left(h\right) a\\
			& h\\
			& & a^{\ast}
		\end{pmatrix}, \algebraicGroup{\aFieldNorm}_{\finiteFieldExtension{2} \slash \finiteField}\left(h\right)\right) \mid a \in \algebraicGroup{A}_{n-1}\,\, h \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \right\}$ \tabularnewline
		\hline		
	\end{tabular}
\end{center}
Here we realize $\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ as $$\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} = \left\{ \left(\begin{pmatrix}
	a & b\\
	db & a
\end{pmatrix}, \lambda\right) \mid a^2 - db^2 = \lambda \in \multiplcativeScheme \right\},$$
where $d$ is as in \Cref{subsec:isometry-groups}.

In the unitary case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{\algebraicGroup{\UnitaryGroup}_n}^{\mathrm{std}}\right)$ is conjugation by $w_n$. In the $\algebraicGroup{\SO}^-_{2n}$ case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{\algebraicGroup{\SO}^{-}_{2n}}^{\mathrm{std}}\right)$ is the outer automorphism on the Dynkin diagram of type $D_n$. In our matrix representation, $\Frobenius$ acts on the Weyl group by conjugation by the matrix $$\left(-n,n\right) \coloneq \begin{pmatrix}\IdentityMatrix{n-1} & 0 & 0 & 0\\
	0 & 1 & 0 & 0\\
	0 & 0 & -1 & 0\\
	0 & 0 & 0 & \IdentityMatrix{n-1}
\end{pmatrix}.$$ In all other cases, the action of $\Frobenius$ on $W(\algebraicGroup{T}_0)$ is trivial. We now parameterize the Weyl group $\Frobenius$-twisted conjugacy classes and their corresponding tori.

\begin{enumerate}
    \item Unitary groups: The Weyl group $W\left(\algebraicGroup{\UnitaryGroup}_n\right)$ is isomorphic to the symmetric group $\SymmetricGroup_n$. If $\dot{w} \in \algebraicGroup{\UnitaryGroup}_n$ is a lift of $w \in W\left(\algebraicGroup{\UnitaryGroup}_n\right)$, the map $w \mapsto \dot{w} \cdot w_n$ sends a $w_n$-twisted $\SymmetricGroup_n$ conjugacy class to a $\SymmetricGroup_n$ conjugacy class. Thus twisted conjugacy classes are determined by the cycle partition $\lambda \vdash n$ associated to $\dot{w} \cdot w_n$. Let us denote by $\lambda^+$ the partition formed by taking the even parts of $\lambda$ and by $\lambda^{-}$ the partition formed by taking the odd parts of $\lambda$. The corresponding algebraic torus is
	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \prod_{i} 	\restrictionOfScalars{\finiteFieldExtension{\lambda^{+}_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \\
	\restrictionOfScalars{\finiteFieldExtension{\lambda_i^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
	% The embedding into the unitary group requires conjugation by \diag(1,1,1,\sqrt{d},\sqrt{d},\sqrt{d}). I would rather not write it.

	%The embedding into $\algebraicGroup{\UnitaryGroup}_n$ is given by the map %\begin{equation}\label{eq:torus-embedding-unitary-group}
	%	\left( \left(g_i\right)_{i=1}^{\lengthof\left(\lambda^+\right)}, \left(h_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}\right) \mapsto \diag(g_1,\dots, g_{\lengthof\left(\lambda^+\right)}, h_1^{\ast}, \dots, h_{\lengthof\left(\lambda^{-}\right)}^{\ast}, \involution{(g^{\ast}_{\lengthof\left(\lambda^+\right)})}, \dots, \involution{(g^{\ast}_1)}).
	%\end{equation}
	See also \cite[Section 2.3]{ThiemVinroot2009} and \cite[Section 2.2]{SaitoShinoda2000}.
    \item (Odd special orthogonal and symplectic groups)
    For $\algebraicGroup{\Sp}_{2n}$ or $\algebraicGroup{\SO}_{2n+1}$, the Weyl group is isomorphic to $$\left\{\pm 1\right\}^n \rtimes \SymmetricGroup_n,$$ which we can identify with the group signed permutations. The conjugacy classes of the Weyl group are classified by pairs of partitions $(\lambda^+,\lambda^-)$ with $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$. See \cite[Section 2.2]{KonvalinkaMatjavPfeiffer2011} for more details. Let $(\lambda^+,\lambda^-)$ correspond to the conjugacy class of $w$ in the Weyl group. Then
		$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
		See also \cite[Section 3.2 Part (B)]{Zalesski2018}.
        \item (Even special orthogonal groups) The Weyl group of $\algebraicGroup{SO}_{2n}^{\pm}$ is isomorphic to $$\left\{ \left(x_1,\dots,x_n\right) \in \left\{\pm 1\right\}^n \mid \prod_{i=1}^n x_i = 1\right\} \rtimes \SymmetricGroup_n,$$ which can be realized the subgroup of the group of signed permutations, consisting of all even signed permutations. Using this realization, we may attach to $w$ in the Weyl group a pair of partitions $\left(\lambda^+, \lambda^-\right)$ as before, with $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$. If $\lambda^{-}$ is not the empty partition, the pair $\left(\lambda^+, \lambda^-\right)$ determines the conjugacy class of $w$. Otherwise, there are two different conjugacy classes of the Weyl group corresponding to the same pair $\left(\lambda^{+}, \lambda^{-}\right)$. These two conjugacy class correspond to isomorphic tori, and these tori are not conjugate in $\algebraicGroup{\SO}_{2n}^{\pm}$. See \cite[Section 2.3]{KonvalinkaMatjavPfeiffer2011} for more details.
        \begin{enumerate}
        	\item (Split case): For $\algebraicGroup{\SO}_{2n}^+$ we have that
        	$$^{L^{-1}w}\algebraicGroup{T}_0 = \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
			See also \cite[Section 3.2 Parts (C) and (D)]{Zalesski2018}.        	
        	\item (Non-split case): As in the unitary group case, for $\algebraicGroup{SO}_{2n}^-$, the map $w \mapsto \dot{w}\circ (-n,n)$ sends a $(-n,n)$-twisted conjugacy class in the even signed permutation group to a conjugacy class in the signed permutation group. Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $\dot{w} \circ (-n,n)$. Then
        	$$^{L^{-1}w}\algebraicGroup{T}_0 = \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
			See also \cite[Section 3.2 Part (D)]{Zalesski2018}. Notice that we differ from that \cite{Zalesski2018} since we do not incorporate the element $\left(-n, n\right)$ in the Frobenius root.
        \end{enumerate}
    \end{enumerate}
	We summarize all these cases in the following theorem.
